\textbf{Case Studies II - Community Talks}

### 2013-04-09 ricardogarfe/final_report/005-gnu-project-community-talk.tex
Update 005-gnu-project-community-talk.tex

\subsection{Techonologies}

\par All projects inside GNU universe share a homogeneous structure and tools to contribute. A part from common techonoligies they use specific tools for each project, depending of the tool purpose.

@@

\par We apply this structure to an existing GNU project: \href{http://www.gnu.org/software/recutils/}{GNU Recutils}and see how easy is to get all starter information.

@@

\par In an overall picture youcan recognize this structure:

\begin{itemize}
	\item \textit{RMS} - Appoints maintainers. \textit{"GNUism"}.
	\item \textit{GNU Advisory Committe} (2009) - Advisory, communication, transversal vision, external contact. advisory@gnu.org. 8 people, most maintainers and FSF America and Europe vice-presidents.
	\item \textit{Maintainers} - Maintainer, lead program development. Follow \href{http://www.gnu.org/prep/maintain_toc.html}{GNU policies for maintainers}.
	\item \textit{Contributors} - Developers with or without commit access.
\end{itemize} You start in the last point as a contributor with ot without commit access, because GNU is not only writting code. There are many areas: documentation, translations, blogging, law, in which where you can be more helpfull that you think. Take a tour in \href{http://www.gnu.org/help/}{How to help GNU}.

@@

\par Starting from these test releases to get an inmersion in the project and know its architecture. This starting point is very important for FLOSS project because is an starting mentoring guide through the code and project structure.

>>>>

\subsection{Technologies}

\par All projects inside GNU universe share a homogeneous structure and tools to contribute. A part from common technologies they use specific tools for each project, depending of the tool purpose.

@@

\par We apply this structure to an existing GNU project: \href{http://www.gnu.org/software/recutils/}{GNU Recutils} and see how easy is to get all starter information.

@@

\par In an overall picture you can recognize this structure:

\begin{itemize}
	\item \textit{RMS} - Appoints maintainers. \textit{"GNUism"}.
	\item \textit{GNU Advisory Committee} (2009) - Advisory, communication, transversal vision, external contact. advisory@gnu.org. 8 people, most maintainers and FSF America and Europe vice-presidents.
	\item \textit{Maintainers} - Maintainer, lead program development. Follow \href{http://www.gnu.org/prep/maintain_toc.html}{GNU policies for maintainers}.
	\item \textit{Contributors} - Developers with or without commit access.
\end{itemize} You start in the last point as a contributor with or without commit access, because GNU is not only writing code. There are many areas: documentation, translations, blogging, law, in which where you can be more helpful that you think. Take a tour in \href{http://www.gnu.org/help/}{How to help GNU}.

@@

\par Starting from these test releases to get an immersion in the project and know its architecture. This starting point is very important for FLOSS project because is an starting mentoring guide through the code and project structure.
